---
title: "Participant Dropout"
author: "Luran M."
date: "July 10, 2019"
output: html_document
---

```{r setup, include=FALSE}

library(knitr, warn.conflicts = F, quietly = T)
library(tidyr, warn.conflicts = F, quietly = T)
library(dplyr, warn.conflicts = F, quietly = T)
library(ggplot2, warn.conflicts = F, quietly = T)
library(keyringr, warn.conflicts = F, quietly = T)
library(redcapAPI, warn.conflicts = F, quietly = T)
library(REDCapR, warn.conflicts = F, quietly = T)
library(lubridate, warn.conflicts = F, quietly = T)

#Create path to and api link to RedCaps
# # https://cran.r-project.org/web/packages/keyringr/vignettes/Avoiding_plain_text_passwords_in_R_with_keyringr.html
credential_label <- "beach_api"
credential_path <- paste(Sys.getenv("USERPROFILE"), '\\DPAPI\\passwords\\', Sys.info()["nodename"], '\\', credential_label, '.txt', sep="")
uri <- "https://redcap.ctsi.ufl.edu/redcap/api/"
beach_token<-decrypt_dpapi_pw(credential_path)

# Create connections
rcon <- redcapConnection(url=uri, token=beach_token)


# crc variables

desired_fields_dropped=c("beach_part_drop_out","beach_last_visit","mom2wk_mod","mom3t_prepreg_bmi","mom3t_delivery_location","inf2wk_delivery_location","mom3t_todays_date","mom2wk_todays_date","mom2mo_todays_date")

# combine desired fields and import test_id and redcap_event_name

desired_fields_all=c(desired_fields_dropped,"test_id","redcap_event_name")

# events to retain

events_to_retain  <- c("third_trimester_arm_1", "two_week_arm_1", "two_month_arm_1","baseline_arm_1")

# consented records

consent.records.v1=c("BLS006A","BLS010A","BLS015A","BLS026A","BLS029A","BLS037A","BLS039A","BLS050A","BLS054A","BLS001A")

# pull data
ds_some_rows_v1<- redcap_read(
  batch_size=300,
  records= consent.records.v1,
  redcap_uri = uri, 
  token      = beach_token, 
  fields     = desired_fields_all,
  events     = events_to_retain
  )$data

head(ds_some_rows_v1)
```

## Did Participant drop:
```{r echo=FALSE}
participant_dropped<-ds_some_rows_v1%>%
  select(test_id,beach_part_drop_out,redcap_event_name)%>%
  filter(redcap_event_name=="baseline_arm_1",beach_part_drop_out==1)%>%
  rename("Dropped Particpants"=test_id)%>%
  select("Dropped Particpants")
kable(participant_dropped)
apple<-c()
for(i in 1:nrow(participant_dropped))
  apple<-c(apple,participant_dropped[i,1])
print(apple)
```

##Last visit completed by participant:
```{r echo=FALSE}
last_visit<-ds_some_rows_v1%>%
  select(test_id,beach_part_drop_out,beach_last_visit,redcap_event_name)%>%
  filter(beach_part_drop_out==1,redcap_event_name=="baseline_arm_1")

for(i in 1:nrow(last_visit)){
  cat(last_visit[i,1])
  if(last_visit[i,3]==1)
    cat("\tlast visit : third trimester\n")
  else if(last_visit[i,3]==2)
    cat("\tlast visit : 2 week\n")
  else if(last_visit[i,3]==3)
    cat("\tlast visit : 2 month\n")
  else if(last_visit[i,3]==2)
    cat("\tlast visit : 6 month\n")
  else if(last_visit[i,3]==2)
    cat("\tlast visit : 12 month\n")
}

```

##Last visit date
```{r echo=FALSE}
#last_visit_date<-ds_some_rows_v1%>%
#  select(test_id,mom3t_todays_date,mom2wk_todays_date,mom2mo_#todays_date,redcap_event_name)
#  
#
#
#for(i in 1:nrow(last_visit)){
#  cat(last_visit[i,1])
#  if(last_visit[i,3]==1){
#    cat("\tlast visit : third trimester\n")
#    last_3t<-last_visit_date%>%select(test_id,mom3t_todays_da#te,redcap_event_name)%>%
#      filter(redcap=="third_trimester_arm_1",test_id==last_vi#sit[i,1])
#    cat(last_3t[1,2])
#  }
#    else if(last_visit[i,3]==2){
#    cat("\tlast visit : 2 week\n")
#  }
#    else if(last_visit[i,3]==3){
#    cat("\tlast visit : 2 month\n")
#  }
#    else if(last_visit[i,3]==2){
#    cat("\tlast visit : 6 month\n")
#  }
#    else if(last_visit[i,3]==2){
#    cat("\tlast visit : 12 month\n")
#  }
#}

```
##Mode of delivery for participant:
###  (If participant did not reach the 2-week visit they will not display because they did not respond to this question)

```{r echo=FALSE}
test<-ds_some_rows_v1%>%
  select(test_id,beach_part_drop_out,redcap_event_name)%>%
  filter(beach_part_drop_out==1,redcap_event_name=="baseline_arm_1")%>%
  distinct(test_id)

apple<-c()
for(i in 1:nrow(test)){
  apple<-c(apple,test[i,1])
}

mode_delivery<-ds_some_rows_v1%>%
  select(test_id,beach_part_drop_out,beach_last_visit, mom2wk_mod,redcap_event_name)%>%
  filter(test_id%in%apple, redcap_event_name=="two_week_arm_1")%>%
  select(test_id,mom2wk_mod)%>%
  distinct(test_id,mom2wk_mod)

for(i in 1:nrow(mode_delivery)){
  cat(mode_delivery[i,1])
  if(is.na(mode_delivery[i,2]))
    cat("\tDid not respond as to mode of delivery\n")
  else if(mode_delivery[i,2]==1)
    cat("\tDelivered : Vaginaly\n")
  else if(mode_delivery[i,2]==2)
    cat("\tDelivered : Cesarean\n")
}

```

##Pre-pregnant BMI of dropped participants:
```{r echo=FALSE}
BMI <- ds_some_rows_v1%>%
  select(test_id,mom3t_prepreg_bmi,redcap_event_name)%>%
  filter(test_id%in%apple,redcap_event_name=="third_trimester_arm_1")%>%
  select(test_id,mom3t_prepreg_bmi)%>%
  rename("participant"=test_id,"pre-Pregnant BMI"=mom3t_prepreg_bmi)
kable(BMI)

```

##Where participant was planning to Deliver during 3rd Trimester:

```{r echo=FALSE}

#chart of Delivery location question at 3rd trimester   
DeliveryLocation_tri <-ds_some_rows_v1%>%
  select(test_id,redcap_event_name,mom3t_delivery_location)%>%
  arrange(test_id,redcap_event_name)%>%
  filter(test_id%in%apple,redcap_event_name == "third_trimester_arm_1")%>%
  select(test_id,mom3t_delivery_location)

for(i in 1:nrow(DeliveryLocation_tri)){
  cat(DeliveryLocation_tri[i,1])
  if(is.na(DeliveryLocation_tri[i,2]))
    cat("\tDid not respond\n")
  else if(DeliveryLocation_tri[i,2]==1)
    cat("\tPlanning to Delivered in UF/Shands\n")
  else if(DeliveryLocation_tri[i,2]==2)
    cat("\tPlanning to Deliver in North Florida Regional\n")
  else if(DeliveryLocation_tri[i,2]==3)
    cat("\tPlanning to Deliver in Birth and Wellness Center of Gainesville\n")
  else if(DeliveryLocation_tri[i,2]==4){
    cat("\tPlanning to Deliver in North Florida Regional\n")
}
  else if(DeliveryLocation_tri[i,2]==5)
    cat("\tResponded that they don't know where they will Deliver\n")
}
#Talbe of participants who responsed to the question
```

##Where particpant Delivered and responded at 2-week visit:
###(Only displays participants that completed the 2-week visit)
```{r echo=FALSE}
DeliveryLocation_tri_pop<-filter(DeliveryLocation_tri,!is.na(mom3t_delivery_location))

#chart of Delivery location question at 2 week

DeliveryLocation_wk <-ds_some_rows_v1%>%
  select(test_id,redcap_event_name,inf2wk_delivery_location___1:inf2wk_delivery_location___5,beach_part_drop_out)%>%
  arrange(test_id,redcap_event_name)%>%
  rename("UFHealth"=inf2wk_delivery_location___1,
         "North Florida Regional"=inf2wk_delivery_location___2,
         "Birth & wellness Center of Gainesville"=inf2wk_delivery_location___3,
         "other"=inf2wk_delivery_location___4,
         "IDK"=inf2wk_delivery_location___5)%>%
  filter(redcap_event_name == "two_week_arm_1",test_id%in%apple)%>%
  rename(participant=test_id,"visit type"=redcap_event_name)

#seperate variables and check for population 

for(i in 1:nrow(DeliveryLocation_wk)){
  cat(DeliveryLocation_wk[i,1])
  if(DeliveryLocation_wk[i,3]>0)
    cat("\tDelivered in  UF\n")  
  else if(DeliveryLocation_wk[i,4]>0)
    cat("\tDelivered in  North Florida\n")  
  else if(DeliveryLocation_wk[i,5]>0)
    cat("\tDelivered in Gainesville Birth and Wellness Center\n")  
  else if(DeliveryLocation_wk[i,6]>0){
    cat("\t Delivered in other\n")
  }
  else if(DeliveryLocation_wk[i,7]>0)
    cat("\tDoes not know location of delivery\n")  
  else
    cat("\tParticipant Didn't respond in questionare\n")    
    }
```

